### 2019-09-30 conflog.tex
bachman edits
edits to satisfy SSC requirements and feedback - Nate

\subsubsection{I Hotel}
Dinner on Friday night will be hosted at the I Hotel. The I Hotel is undergoing an expansion that will increase the capacity of their banquet space to 690 people in rounds. Catering is provided by University Catering which avoids a 20\% gratuity charge because of its association with the University of Illinois. This expansion is set to be completed by Fall 2020. We will be hosting a social at the 77 Club in Memorial Stadium, just up the street. Information about the I Hotel expansion is included in Appendix D.

@@

$\textbf{The Garden Hotel Urbana}$\\
When selecting the primary hotel to accommodate students we considered the ability to host all students under one roof over proximity to the conference activities. The Garden Hotel Urbana (soon to be the Radisson) will be the primary hotel for all attendees. This will also be the location of the opening ceremony dinner. Since this hotel is just beyond walking distance from the main conference activities, we will hire four Peoria Charter busses to shuttle attendees to and from the Union every 10 minutes. Additionally, there is a CU-MTD bus stop adjacent to the hotel that travels directly to the Union and runs every 10 minutes from 8am to 6pm. \\ 
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{garden_king.jpg}
		\subcaption{King Suite}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{garden_queen.jpg}
		\subcaption{Queen Double}
	\end{subfigure}
	\caption{Garden Urbana Hotel rooms}		
\end{figure}

@@

$\textbf{Marriott TowneSuites}$\\
In the event that attendance exceeds 600 people, we will have overflow rooms in the Marriott TowneSuites. Rooms at the Marriott resemble a studio apartment with an open floor plan, refrigerator, stove, microwave,dishes, and dining area. Many rooms are equipped with pull-out couches, allowing 5 students to share a queen double room if desired. The hotel offers internet access for a maximum of 3 devices per room. The hotel is located on Green Street and the Illini Union a mere five-minute walk away. For $\$7$ a day, guests may park in a parking garage with 8ft clearance.\\
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{marriott_room1.jpeg}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{marriott_room2.jpeg}
	\end{subfigure}
	\caption{Marriott Rooms: Left, a queen double. Right, a king single}		
\end{figure}

UIUC is one of most well represented schools at past student conferences. Students from UIUC will be able to stay in their respective dorms and apartments to maximize the number of hotel rooms available to out of town guests.

\begin{table}
\caption{Cost of Hotels}
\label{table:hotels}
	\centering
	\makebox[0.6\linewidth]{\begin{tabular}{lccccc}
	\hline\hline
	\textbf{Hotel} & \textbf{Distance from the Union (mi)} & \textbf{Dates} & \textbf{Number of Rooms} & \textbf{Rates*} & \textbf{Per Person**}\\
	\hline\hline
	Garden Urbana & 2.2  & 4/8-4/11 & 198 & 119 & $\$$29.75\\
	Illini Union & 0.0 & 4/8-4/11 & 35 & 134 & $\$$33.5\\
	Marriott TowneSuites &0.25 & 4/8-4/11 & 95 & 189 & \$47.50\\ 
	\hline
	\end{tabular}}
\end{table}
\textbf{*}\textit{Price for a queen double}
\textbf{**}\textit{Assumes 4 people per room}

@@

\textbf{Thursday Night}\\
Communicating the science of nuclear energy remains one of the chief challenges of our field. The opening dinner of this conference will focus on science communication and the people behind the science. Science communication requires more than the recitation of raw data to be effective. By telling our own, diverse backstories, we become more effective science communicators. Speakers will be asked to speak to their own backstory as a nuclear advocate and how their story makes them a more effective communicator.\\\\
\indent\textbf{Friday Night}\\
The second dinner will be themed around networking and professional-development and how these critical tools have value beyond finding jobs. Communities like ANS thrive on the exchange of ideas and knowledge. The student conference serves plays an essential role by connecting the burgeoning minds of the next generation with the wisdom of established professionals. This dinner will consist of tables organized by company/national lab to allow students and professionals to mingle, promoting the exchange of ideas.\\\\ 
\indent\textbf{Saturday Night}\\
The closing dinner of the conference will be a call to action for student attendees. Ours is a generation faced with challenges on a scale never witnessed by humanity, and we will only successfully address these challenges through the engagement of as many bright young minds as possible. The speakers for this night will be asked to address ways we all can take individual responsibility for the grand challenges of our age by using our own unique skills to tackle problems like climate change and energy poverty from every angle imaginable.\\ 
\subsection{Travel and Transportation}

\subsubsection{Getting to Champaign}
The University of Illinois is a 2.5 hour drive from one of the largest airports in the world, O'Hare International Airport. There is also a small airport located just 20 minutes outside of campus. Additionally, there is a reliable bus service, Peoria Charter, that runs between O'Hare and the UIUC campus several times per day. Table \ref{table:airfare} shows the round-trip, non-stop, airfare costs for the first weekend of April. Peoria Charter fare from O'Hare to UIUC is currently $\$61$ round-trip. Due to the central location of UIUC, driving might be a good option for some schools and individuals. Table \ref{table:ground} shows the approximate driving times and costs from several universities.

>>>>

\subsubsection{I Hotel}
Dinner on Friday night will be hosted at the I Hotel. The I Hotel is undergoing an expansion that will increase the capacity of their banquet space to 690 people in rounds. Catering is provided by University Catering which avoids a 20\% gratuity charge because of its association with the University of Illinois. This expansion is set to be completed by Fall 2020. We will be hosting a social at the 77 Club in Memorial Stadium, which is just a brief walk up the street. Information about the I Hotel expansion is included in Appendix D. Cost of transportation to and from the I Hotel and 77 Club are discussed in the budget section.

@@

$\textbf{The Garden Hotel Urbana}$\\
When selecting the primary hotel to accommodate students we considered the ability to host all students under one roof over proximity to the conference activities. The Garden Hotel Urbana (soon to be the Radisson) will be the primary hotel for all attendees. It features complimentary breakfast for its guests every morning. This will also be the location of the opening ceremony dinner. Since this hotel is just beyond walking distance from the main conference activities (2.2 miles), we will hire four Peoria Charter busses to shuttle attendees to and from the Union every 10 minutes. Additionally, there is a CU-MTD bus stop adjacent to the hotel that travels directly to the Union and runs every 10 minutes from 7am to 5am the following day for weekdays, and every 30 minutes on weekends. \\ 
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{garden_king.jpg}
		\subcaption{King Suite}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{garden_queen.jpg}
		\subcaption{Queen Double}
	\end{subfigure}
	\caption{Garden Urbana Hotel rooms}		
\end{figure}

@@

$\textbf{Marriott TowneSuites}$\\
The Marriott TowneSuites is the professional's designated hotel; and, in the event that attendance exceeds 600 people, we will have overflow rooms in the Marriott TowneSuites. Rooms at the Marriott resemble a studio apartment with an open floor plan, refrigerator, stove, microwave,dishes, and dining area. Many rooms are equipped with pull-out couches, allowing 5 students to share a queen double room if desired. The hotel offers internet access for a maximum of 3 devices per room. The hotel is located on Green Street and the Illini Union a mere five-minute walk away. For $\$7$ a day, guests may park in a parking garage with 8ft clearance.\\
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{marriott_room1.jpeg}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{marriott_room2.jpeg}
	\end{subfigure}
	\caption{Marriott Rooms: Left, a queen double. Right, a king single}		
\end{figure}

UIUC is one of most well represented schools at past student conferences. Students from UIUC will be able to stay in their respective dorms and apartments to maximize the number of hotel rooms available to out of town guests. Sections seeking travel assistance are required to use the room blocks described above to prevent extra costs. Another proposed method to alleviate costs is to allow an option for students from smaller sections to be housed at an ANS-UIUC section member's apartment. The Diversity co-chair will assume responsibilities of reaching out to members-at-large and other minority serving institutions.

\begin{table}
\caption{Cost of Hotels}
\label{table:hotels}
	\centering
	\makebox[0.6\linewidth]{\begin{tabular}{lccccc}
	\hline\hline
	\textbf{Hotel} & \textbf{Distance from the Union (mi)} & \textbf{Dates} & \textbf{Number of Rooms} & \textbf{Rates*} & \textbf{Per Person**}\\
	\hline\hline
	Garden Urbana & 2.2  & 4/8-4/11 & 198 & 119 & $\$$29.75\\
	Illini Union & 0.0 & 4/8-4/11 & 35 & 134 & $\$$33.5\\
	Marriott TowneSuites &0.25 & 4/8-4/11 & 95 & 189 & \$47.50\\ 
	\hline
	\end{tabular}}
\subcaption*{\textbf{*}\textit{Price for a queen double} \textbf{**}\textit{Assumes 4 people per room}}
\end{table}

@@

\textbf{Thursday Night}\\
Communicating the science of nuclear energy remains one of the chief challenges of our field. The opening dinner of this conference will focus on science communication and the people behind the science. Science communication requires more than the recitation of raw data to be effective. By telling our own, diverse backstories, we become more effective science communicators. Speakers will be asked to speak to their own backstory as a nuclear advocate and how their story makes them a more effective communicator.\\\\
\indent\textbf{Friday Night}\\
The second dinner will be themed around networking and professional-development and how these critical tools have value beyond finding jobs. Communities like ANS thrive on the exchange of ideas and knowledge. The student conference serves plays an essential role by connecting the burgeoning minds of the next generation with the wisdom of established professionals. This dinner will consist of tables organized by company/national laboratory or by topic/discipline area to allow students and professionals to mingle, promoting the exchange of ideas.\\\\ 
\indent\textbf{Saturday Night}\\
The closing dinner of the conference will be a call to action for student attendees. Ours is a generation faced with challenges on a scale never witnessed by humanity, and we will only successfully address these challenges through the engagement of as many bright young minds as possible. The speakers for this night will be asked to address ways we all can take individual responsibility for the grand challenges of our age by using our own unique skills to tackle problems like climate change and energy poverty from every angle imaginable.\\ 
\subsection{Travel and Transportation}

\subsubsection{Getting to Champaign}
The University of Illinois is a 2.5 hour drive from one of the largest airports in the world, O'Hare International Airport. There is also a small airport located just 20 minutes outside of campus. Additionally, there is a reliable bus service, Peoria Charter, that runs between O'Hare and the UIUC campus several times per day. Table \ref{table:airfare} shows the round-trip, non-stop, airfare costs for the first weekend of April. Peoria Charter fare from O'Hare to UIUC is currently $\$61$ round-trip. While travel from airport to hotel can be managed by train (Amtrak/Metra), the conference planning committee excluded this option due to the added complexities of getting from the airport to train station, and train station to hotel with the associated costs of doing so. We believe the charter bus to be the best route of action as it picks up travelers directly at the arrivals gate and brings them to the Illini Union. Due to the central location of UIUC, driving might be a good option for some schools and individuals. Table \ref{table:ground} shows the approximate driving times and costs from several universities.
